SunPy - Python for Solar Physics

### 2014-01-28 2-3-Spectra.tex
minor edits to Spectra section

SunPy aims to provide broad support for solar spectroscopy
instruments.  The variety and complexity of these instruments and
their resultant datasets makes it very challenging to support all in a
general way.  The \texttt{spectra} module implements a
\texttt{Spectrum} class for 1D data (intensity versus frequency) and a
\texttt{Spectrogram} class for 2D data (intensity versus time and
frequency).  Each of these classes use a \texttt{numpy.ndarray} class
as its \texttt{.data} attribute.  These two classes were implemented
by funding provided by the Astrophysics Research Group at Trinity
College Dublin, Ireland.

@@

Listing \ref{code:spectra} shows how the \texttt{CallistoSpectrogram}
object retrieves spectrogram data in the time range specified taken at
the observatory of interest.  When the data is requested using the
\texttt{.from\_range} function, the object merges all the downloaded
files downloaded into a single spectrogram, across time and frequency.
In the example shown, data is observed in two frequency ranges, 
20--90\,MHz and 55--355\,MHz.  Since the data is not evenly spaced in
the frequency range, the \texttt{Spectrogram} object linearises the
frequency axis for a better analysis.  The example also demonstrates
the implemented background subtraction method.
%ji to DPS - what is the linearisation that is happening here?

>>>>

SunPy aims to provide broad support for solar spectroscopy
instruments.  The variety and complexity of these instruments and
their resultant datasets makes this a challenging goal.  The \texttt{spectra} module implements a
\texttt{Spectrum} class for 1D data (intensity versus frequency) and a
\texttt{Spectrogram} class for 2D data (intensity versus time and
frequency).  Each of these classes use a \texttt{numpy.ndarray} class
as its \texttt{.data} attribute.  These two classes were implemented
by funding provided by the Astrophysics Research Group at Trinity
College Dublin, Ireland.

@@

Listing \ref{code:spectra} shows how the \texttt{CallistoSpectrogram}
object retrieves spectrogram data in the time range specified taken at
the observatory of interest.  When the data is requested using the
\texttt{.from\_range} function, the object merges all the downloaded
files into a single spectrogram, across time and frequency.
In the example shown, data is provided in two frequency ranges, 
20--90\,MHz and 55--355\,MHz.  Since the data is not evenly spaced in
the frequency range, the \texttt{Spectrogram} object linearises the
frequency axis for a better analysis.  The example also demonstrates
the implemented background subtraction method.
%ji to DPS - what is the linearisation that is happening here?
